\papertitle

### 2014-03-20 final-report/paper.tex
Sloppy

\begin{abstract}

We propose \system, a visualization tool that helps database developers
explore and understand query execution and data movement in a distributed
database management system (DDBMS). \system provides quick insight into common
problems such as data skew or performance bottleneck by leveraging
visualization techniques to present: (1) data flow between query operators and
between workers, (2) query execution and operator dependencies, (3) cluster
utilization, (4) network utilization.

In particular, \system is built to inspect query execution in Myria~\cite{myria},
a distributed big data management system currently being developed in the
UW CSE database group. Myria aims towards building a distributed database
platform to provide \emph{big data management and analytics as a service} primarily
for scientific applications. The proposed visualizations can easily be applied to
other DDBMS as well (e.g. Spark, Hadoop).

>>>>

\begin{abstract}
\sloppy
We propose \system, a visualization tool that helps database developers explore
and understand query execution and data movement in a distributed database
management system. \system provides quick insight into common problems
such as data skew or performance bottleneck by leveraging visualization
techniques to present: (1) data flow between query operators and between
workers, (2) query execution and operator dependencies, (3) cluster
utilization, (4) network utilization.

\sloppy
In particular, \system is built to inspect query execution in Myria~\cite{myria},
a distributed big data management system currently being developed in the
UW CSE database group. Myria aims towards building a distributed database
platform to provide \emph{big data management and analytics as a service} primarily
for scientific applications. The proposed visualizations can easily be applied to
other DDBMS as well (e.g. Spark, Hadoop).
